%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Do not alter this block (unless you're familiar with LaTeX
\documentclass[12pt]{article}
\usepackage[margin=5cm]{geometry} 
\usepackage{amsmath,amsthm,amssymb,amsfonts, fancyhdr, color, comment, graphicx, environ}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage[shortlabels]{enumitem}
\usepackage{indentfirst}
\usepackage{hyperref}
\usepackage{tensor}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
}
\usepackage{tikz-cd}
\tikzset{ampersand replacement = \&}
\pagestyle{fancy}

\usepackage{tikz}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=1.2pt] (char) {#1};}}
            
    

\newenvironment{problem}[2][Problem]
    { \begin{mdframed}[backgroundcolor=gray!20] \textbf{#1 #2} \\}
    {  \end{mdframed}}

% Define solution environment
\newenvironment{solution}
    {{\textbf{Solution}}}

\newcommand{\numbox}[2]{$^{\circled{#1}}${\fbox{#2}}}





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Fill in the appropriate information below
\lhead{PHIL131.01 \\ Assignment-1}
\rhead{Atahan \\ Haznedar} 
\chead{\textbf{2021107075}}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

    \begin{problem}{(1)}
        You should do well, since you have talent and you are a hard worker.
    \end{problem}
    
    \begin{solution}
        \numbox{1}{You should do well,} since \numbox{2}{you have talent} and  \numbox{3}{you are a hard worker.}\\
    
        
            \begin{center}
                \begin{tikzcd}[every matrix/.append style={name=mymatr},row sep=1.5em,column sep=0.3em, execute at end picture={\draw (mymatr-1-1.south west) -- (mymatr-1-3.south east);}]
                    {2} \& {+} \arrow{d} \& {3}  \\
                    {} \& 1 \& {} \\
                \end{tikzcd}
            \end{center}

        
    \end{solution}
    
    
    \begin{problem}{(3)}
        We need more morphine. We’ve got 32 casualties and only 12 doses of morphine left.
    \end{problem}
    
    \begin{solution}
        \numbox{1}{We need more morphine.} \numbox{2}{We’ve got 32 casualties} and \numbox{3}{only 12 doses of morphine left.}\\
        
            \begin{center}
                \begin{tikzcd}[every matrix/.append style={name=mymatr},row sep=1.5em,column sep=0.3em, execute at end picture={\draw (mymatr-1-1.south west) -- (mymatr-1-3.south east);}]
                    {2} \& {+} \arrow{d} \& {3}  \\
                    {} \& 1 \& {} \\
                \end{tikzcd}
            \end{center}
    \end{solution}

\clearpage

    \begin{problem}{(15)}
        Neither the butler nor the maid did it. That leaves the chauffeur or the cook. But the chauffeur was 
        at the airport when the murder took place. The cook is the only one without an alibi for his whereabouts. Moreover, the heiress was poisoned. It’s logical to conclude that the cook did it.
    \end{problem}
    
    \begin{solution}
        \numbox{1}{Neither the butler nor the maid did it.} \numbox{2}{That} \fbox{leaves the chauffeur or the cook.} But \numbox{3}{the chauffeur was at} \fbox{the airport when the murder took place.} \numbox{4}{The cook is the} \linebreak \fbox{only one without an alibi for his whereabouts.} Moreover, \linebreak \numbox{5}{the heiress was poisoned.} \numbox{6}{It’s logical to conclude that} \linebreak\fbox{the cook did it.}

        
    



        
            \begin{center}
                \begin{tikzcd}[every matrix/.append style={name=mymatr},row sep=1.5em,column sep=0.3em, execute at end picture={\draw (mymatr-2-1.south west) -- (mymatr-2-7.south east);}]
                    {1} \arrow{d} \& {} \& {} \& {} \& {} \& {} \& {}  \\
                    {2} \& {+} \& {3} \& {+}\arrow{d} \& {4} \& {+} \& {5}  \\
                    {} \& {} \& {} \& {6} \& {} \& {} \& {}  \\
                \end{tikzcd}
            \end{center}

    \end{solution}

\clearpage

    \begin{problem}{2}
        The term man may designate either all human beings or only those who are adult and male.
    \end{problem}
    
    \begin{solution}
        The term 'man' may designate either all human beings or only those who are adult and male.
    \end{solution}
    
    \begin{problem}{4}
        Rome is known by the name the Eternal City. The Vatican is in Rome. Therefore, the Vatican is in 
        the Eternal City.
    \end{problem}
    
    \begin{solution}
        Rome is known by the name the Eternal City. The Vatican is in Rome. Therefore, the Vatican is in 
        the Eternal City.
    \end{solution}
    
    \begin{problem}{6}
        In formal logic, the letters P and Q are often used to designate propositions.
    \end{problem}
    
    \begin{solution}
        In formal logic, the letters 'P' and 'Q' are often used to designate propositions.
    \end{solution}

    
    


\end{document}